\sysfull

### 2017-11-17 paper/evaluation.tex
eval: match the legend: NONE
explain the blue section of a page fault bar

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalStrategies}
	\caption{\textbf{\sys coalescing strategies performance per application on intermittent power compared to \sys without coalescing (`NO').}}
%\todo{Change WHD to TSHC and HD to HC}{Amjad}}
	\label{fig:coalescing}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/ramPagsSizes}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\textbf{\sys normalized runtime for various page sizes, \{32, 64, $\ldots$,1024\}\,bytes, per application (top) and respective page faults (bottom)}; X = zero page faults.}
%\todo{change X to 0, remove the definition of X from caption}{Amjad}}
	\label{fig:page_size}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalStrategies}
	\caption{\textbf{\sys coalescing strategies performance per application on intermittent power compared to \sys without coalescing (`NONE').}}
%\todo{Change WHD to TSHC and HD to HC}{Amjad}}
	\label{fig:coalescing}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/ramPagsSizes}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\textbf{\sys normalized runtime for various page sizes, \{32, 64, $\ldots$,1024\}\,bytes, per application (top) and respective page faults (bottom)}; X = zero page faults; the blue section of a bar represents a full page swap (replacing pages in both FRAM and SRAM).}
%\todo{change X to 0, remove the definition of X from caption}{Amjad}}
	\label{fig:page_size}
\end{figure}
